Metadata for ``Spin canonical rings of log stacky curves''

### 2016-02-23 curves-write-up/AIF/spin-cring-metadata.tex
curves: first french translations

\title{Summary of Changes in response to Referee's Report}
\author{Aaron Landesman, Peter Ruhm, and Robin Zhang}

@@

\maketitle
\section{Changes Made}
Here are the changes we have made in response to the referee's suggestions.

\begin{enumerate}
	\item In response to referee comment (1), we added Remark 2.6 on Gorensteinness of the log canonical ring following
	the definition of a log spin canonical ring in the background section.
	We noticed that the referee made a comment saying
	``Cohen-Macaulay and
projectively Gorenstein follows as usual (of course, provided there are
no log canonical points).'' We were a bit confused about the parenthetical, but interpreted
it to mean that the canonical ring may not be Gorenstein if it is of the form
\begin{align*}
	\oplus_n H^0(X, P + n L)
\end{align*}
for $L$ some fractional divisor and $P$ a point. Of course, in our paper, all canonical rings are of the form
\begin{align*}
	\oplus_n H^0(X, n L)
\end{align*}
for $L$ a fractional divisor, so this would not pose an issue.
	\item In response to referee comment (2), we included Hilbert polynomials in Examples $3.3- 3.6$.
		Throughout we reference Theorem 4.2.1 of Zhou's thesis,
		but also include remark 3.2 explaining that we could also use
		Theorem 3.1 of Buckley, Reid, and Zhou's paper.
	\item In response to referee comment (3), we included a Remark 2.11 on the existence of generators in degree $0 \bmod r_i$
		and $-2 \bmod r_i$ near the end of subsection 2.1.
	\item In response to referee comment (4), we replaced ``best lower approximation'' with Hirzebruch--Jung
		fractions. This not only allowed us to delete the unnecessary, nonstandard definition
		of ``best lower approximation,''
		but also allowed us to shorten and
		clarify our proof of the rather
		technical Lemma 4.4 (which was
		Lemma 4.6 in the previous version).
\end{enumerate}

\section{Other suggestions}
The referee also made the following notational suggestions,
and here we include reasons for why we would prefer not to
implement them.

\begin{enumerate}
	\item Toward the end of referee comment (1), the referee suggests
		to change the notation from $\frac{e_i - 1}{2 e_i}$
		to $\frac{s_i}{2 s_i + 1}$ where $s_i = \frac{e_i - 1}{2}$.
		First, we would like to keep our notation because we often
	list degrees of generation and relations by signatures
	of the form $(g; e_1, \ldots, e_n; \delta)$ with bounds given in
	the form $\min(5, e_1, \ldots, e_n)$. These
	seem simpler to
	consider than enumeration by signatures $(g; s_1, \ldots, s_n;
	\delta)$ with bounds given in the form $\min(5, 2s_1 + 1, \ldots,
	2s_n + 1)$. Second, because we will be using $e_i$
	so frequently in our analysis, the paper is shortened
	by writing $e_i$ instead of $2s_i+1$.
	Third, we maintained the $e_i$ notation for consistency
	with the notation established in Voight--Zureick-Brown.
	Fourth, since one of our main applications is to modular forms,
	number theorists reading the paper may have an easier time
	translating the work to the context of modular curves whose 
	signatures are written with $e_i$ rather than $s_i$.
	\item Prior to referee comment (1), the referee suggests we use 
orbifold terminology instead
		of stacky terminology. 
		One reason we'd like to keep stacky terminology is
		that the results of this paper hold over a finite field,
		and it seems more natural to 
work with	stacks rather than orbifolds in the context of finite fields.
		Also, since this paper is in many
		ways intimately tied with Voight--Zureick-Brown,
		we would like to keep the use of stacky terminology
		in order to remain compatible with that paper.
	\item Prior to referee comment (1), the referee suggests to 
remove the signature invariant
		and use the more general terminology from the
		``ice cream paper''. We agree that it is
		somewhat difficult to generalize the
		signature terminology, but we also note that this signature is
		commonly used in referring
		to modular curves. Since one of the important
		applications of this paper is to rings of modular
		forms, the signature will play a useful role for
		those interested in the translation to modular curves.
		Once again, we would also like to keep the signature
		to remain compatible with Voight--Zureick-Brown.
\end{enumerate}

>>>>

\title{Metadata for ``Spin canonical rings of log stacky curves''}
\author{Aaron Landesman, Peter Ruhm, and Robin Zhang}

@@

\maketitle

\begin{enumerate}
	\item Title (English): Spin canonical rings of log stacky curves \\
		Titre (Fran\c{c}ais): Anneaux log-canoniques de spin des
		courbes de champs alg\'{e}briques
	\item Abstract (English): Consider modular forms arising from a
		finite-area quotient of the upper-half plane by a Fuchsian group.
		By the classical results of Kodaira--Spencer, this ring of
		modular forms may be viewed as the log spin canonical ring of a
		stacky curve. In this paper, we tightly bound the degrees of
		minimal generators and relations of log spin canonical rings.
		As a 	consequence, we obtain a tight bound on the degrees of
		minimal generators and relations for rings of modular forms of
		arbitrary integral weight. \\
		Abstrait (Fran\c{c}ais): Consid\'{e}rez formes modulaires
		d\'{e}coulant d'une quotient d'aire-finie du demi-plan
		sup\'{e}rieur par un groupe fuchsien. Par les r\'{e}sultats
		classiques de Kodaira--Spencer, cet anneau de formes modulaires
		peut \^{e}tre consid\'{e}r\'{e} comme l'anneau log-canonique de
		spin d'un courbe de champs alg\'{e}briques. Dans cet article, nous
		lions \'{e}troitement les degr\'{e}s de g\'{e}n\'{e}rateurs
		minimaux et les relations minimes de l'anneau log-canonique de spin
		d'un courbe de champs alg\'{e}briques. Par conséquent, on obtient
		un virage serr\'{e} li\'{e} sur les degr\'{e}s de
		g\'{e}n\'{e}rateurs minimaux et relations minimes pour les anneaux
		de formes modulaires de poids arbitraires int\'{e}grantes.
  \end{enumerate}
